Effect of quality-adjusted production function inputs

### 2015-05-01 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added rho_1.
Word changes.
Working toward making graphs.

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconData)
require(EconModels)
require(dplyr)

@@

Two other nestings of the factors of production ($k$, $l$, and $e$)
are possible with the CES model.
%
\begin{equation} \label{eq:CESlek}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)}
\end{equation}
%
\begin{equation} \label{eq:CESekl}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)}
\end{equation}
% 
Note that $\rho$ ($\sigma$), $\delta$, and $\delta_1$ have different
meanings that depend upon the nesting of the factors of production.

@@

@@

\begin{table} \caption{Unadjusted variables.} 
\label{tab:unadjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal           & UK                 \\
      \midrule
      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{Unadjusted variables.} 
\label{tab:quality_adjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal         & UK               \\
      \midrule
      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconData)
require(EconModels)
require(dplyr)
require(reshape2)
require(ggplot2)

@@

Two other nestings of the factors of production ($k$, $l$, and $e$)
are possible with the CES model.
%
\begin{equation} \label{eq:CESlek}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)}
\end{equation}
%
\begin{equation} \label{eq:CESekl}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
      A \equiv \mathrm{e}^{\lambda (t-t_0)}
\end{equation}
% 
Note that $\rho$ ($\sigma$), $\rho_1$ ($\sigma_1$), $\delta$, and $\delta_1$ have different
meanings depending upon the nesting of the factors of production.

@@

\begin{table} \caption{Unadjusted time-series variables.} 
\label{tab:unadjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal           & UK                 \\
      \midrule
      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{Quality-adjusted time series variables.} 
\label{tab:quality_adjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal         & UK               \\
      \midrule
      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
mdata <- melt(historicalData, 
              measure.vars = c(as.character(y_PT), 
                               as.character(k_PT_unadj), as.character(l_PT_unadj), as.character(e_PT_unadj),
                               as.character(k_PT_adj), as.character(l_PT_adj), as.character(e_PT_adj),
                               as.character(y_UK), 
                               as.character(k_UK_unadj), as.character(l_UK_unadj), as.character(e_UK_unadj),
                               as.character(k_UK_adj), as.character(l_UK_adj), as.character(e_UK_adj)), 
              variable.name = "variable",
              value.name = "value")
historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ Source, 
               line_types = c(1,5,2,6,4,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1 or 1970=1)")

ggplot(mdata, mapping=aes(x=Year, y=value, group=variable) + 
  geom_line(mapping) +
  facet_grid( facet_formula, scales="free_y" ) + 
  scale_linetype_manual(name="", values=line_types) + 
  xy_theme()

@@
